Frequency of dwarf and massive galaxy pairs in the IllustrisTNG cosmological simulation

### 2023-02-09 paper/pears.tex
adding updated captions

  \begin{figure*}[htb]
    \centering
    \includegraphics[width=\textwidth]{counts.png}
    \caption{Median number of dwarf and massive primaries and pairs per abundance matching realization as a function of redshift, with shaded regions showing the $1^{\rm st}$ and 99$^{\rm th}$ percentiles. The number of dwarf and massive primaries peaks around $z=1$, and there are fewer primaries and pairs at higher redshift, and . The evolution of the number of primaries is roughly similar between dwarf and massive galaxies, though the number of dwarf primaries drops steeply from $z=1$ to $z=0$. The number of dwarf pairs peaks around $z=2$, while the number of massive pairs increases nearly monotonically from $z=4-0$. There are approximately 8 times as many dwarf primaries as massive primaries. 
      }
    \label{fig:counts}
  \end{figure*}

  \begin{figure*}[htb]
    \centering
    \includegraphics[width=\textwidth]{stellarmass_distribution.png}
    \caption{\kc{caption}
      }
    \label{fig:massratio}
  \end{figure*}

@@

\label{sec:results}
\begin{figure*}[htb]
  \centering
  \includegraphics[width=\textwidth]{pairratio.png}
  \caption{Median fraction (and 1-99 percentile shaded regions) of dwarf (green) or massive (pink) primaries with a major (left) or minor (right) companion. The fraction of massive primaries with a major or minor companion remains approximately constant for $z>1$, while at $z<\sim0.5$ the pair fraction increases sharply to $z=0$. However, the pair fraction for dwarf pairs evolves significantly differently to massive galaxy pairs. The fraction of dwarf primaries with a companion is approximately constant for $z>2$, but decreases monotonically from $z=2$ to $z=0$. \kc{include more numbers including the difference between the ratios. "Evolves distinctly"} 
    }
  \label{fig:pairratio}
\end{figure*}

@@

\begin{figure*}[htb]
  \centering
  \includegraphics[width=\textwidth]{separation.png}
  \caption{Median physical separation (in kpc) and 1-99 percentile shaded regions of 1000 abundance matching realizations as a function of redshift for dwarf pairs (left, green), and massive pairs (right, pink). Major pairs (high stellar mass ratio) are shown in solid lines, while minor pairs are depicted with dashed lines. Minor dwarf pairs tend to be $\sim10-20\kpc$ closer than major dwarf pairs, while minor massive pairs are between $10-50\kpc$ closer than major pairs. In general, as the redshift \textit{decreases} toward $z=0$, the average physical separation of a dwarf or massive pair \textit{increases}. The evolution of massive pair separations is approximately linear for $z>1$, increasing sharply for $z<0$, while the evolution of the dwarf pairs closely resembles a power law distrbution across the whole redshift range from $z=0-4$. \kc{add difference plot!}
    }
  \label{fig:sep}
\end{figure*}

\begin{figure*}[htb]
  \centering
  \includegraphics[width=\textwidth]{separation_distribution.png}
  \caption{Normalized physical separation distribution for dwarf and massive pairs (top/green and bottom/pink, respectively) from $z=0$ (left) to $z=3$ (right). Major pairs are shown as solid lines, while minor pairs are dashed. 
  Both dwarf and massive pairs have narrow distributions about low separations at high redshifts, and a wider distribution of separations at lower redshift. 
  \todo{would it be instructive to make this plot, unnormalized, with z=0-3 on same plot to see if low sep pop numbers change drastically}
  Also note than many of the close pairs at high z may merge by $z=0$. \kc{add median line to plot}
    }
  \label{fig:sep-dist}
\end{figure*}

\begin{figure*}[htb]
  \centering
  \includegraphics[width=\textwidth]{velocity.png}
  \caption{Median relative velocity (in \kms) and 1-99 percentile shaded regions of 1000 abundance matching realizations as a function of redshift for dwarf pairs (left, green) and massive pairs (right, pink). Major pairs (high stellar mass ratio) are shown in solid lines, while minor pairs are depicted with dashed lines. Major and minor pairs (in both the dwarf and massive regime) tend to have approximately the same median relative velocity. In addition, as the redshift \textit{decreases} toward $z=0$, the average relative velocity of a pair \textit{decreases} as well. The overall behavior of the redshift evolution is nearly identical for dwarf and massive pairs (though note that the massive pairs have \textit{much} higher relative velocities than the dwarf pairs at all redshifts.)
    }
  \label{fig:vel}
\end{figure*}

\begin{figure*}[htb]
  \centering
  \includegraphics[width=\textwidth]{velocity_distribution.png}
  \caption{
  Normalized velocity distribution for dwarf and massive pairs (top/green and bottom/pink, respectively) from $z=0$ (left) to $z=3$ (right). Major pairs are shown as solid lines, while minor pairs are dashed. 
  The distribution of relative velocities for dwarf and massive pairs move to slightly lower velocities at lower redshifts. The distribution of velocities for major and minor pairs is roughly equivalent. 
  \kc{caption}
    }
  \label{fig:vel-dist}
\end{figure*}

@@

\begin{figure*}[htb]
  \centering
  \includegraphics[width=\textwidth]{scaledsep.png}
  \caption{Median scaled separation (separation of a pair divided by the virial radius of its group) as a function of redshift. Dwarf pairs (major (solid) and minor (dashed)) tend to have smaller scaled separations at lower redshifts, leveling out between $z=0-1$. In particular, the secondaries of dwarf major pairs at $z>2$ tend to live more than one virial radius away from the primary. Massive major pairs at low redshift tend to have smaller scaled separations  at $z<\sim2$, but vary significantly at higher redshifts. 
  Minor pairs (right), both dwarf and massive, tend to have smaller separations, tending to live closer than one virial radius between the primary and secondary. Massive minor pairs tend to have smaller scaled separations compared to dwarf pairs at all redshifts.
    }
  \label{fig:sep-scaled}
\end{figure*}

\begin{figure*}[htb]
  \centering
  \includegraphics[width=\textwidth]{scaledsep_distribution.png}
  \caption{\kc{to write}}
  \label{fig:sep-scaled-dist}
\end{figure*}

\begin{figure*}[htb]
  \centering
  \includegraphics[width=\textwidth]{scaledvel.png}
  \caption{Median scaled velocity (relative velocity of a pair divided by the virial velocity, defined as the circular velocity at the virial radius of the group \todo{need to remove the 2 in the virial radius calc!}) as a function of redshift. 
  Major pairs are on the left (solid lines), minor pairs are on the right in dashed lines.
  All sets of pairs show an increase in scaled velocity at lower redshifts.}
  \label{fig:vel-scaled}
\end{figure*}

\begin{figure*}[htb]
  \centering
  \includegraphics[width=\textwidth]{scaledvel_distribution.png}
  \caption{\kc{to write}}
  \label{fig:vel-scaled-dist}
\end{figure*}

>>>>

  \begin{figure*}[htb]
    \centering
    \includegraphics[width=\textwidth]{counts.png}
    \caption{(Top) Median number of dwarf (left) and massive (right) primaries and pairs per abundance matching realization as a function of redshift.
    Shaded regions show the $1^{\rm st}$ and 99$^{\rm th}$ percentile values of the medians of all realizations. 
    There are approximately 8 times as many dwarf primaries as massive primaries. 
    % dwarf galaxies
    The dwarf primary count (green solid line in top left panel) is at a minimum at $z=4$, rises to a maximum of $\sim15000$ halos per realization by $z=1$, then decreases by $\sim16\%$ to 12000 halos at $z=0$. The dwarf pair count (green dashed line), on the other hand, peaks at $z\sim2$ with 3000 pairs, and decreases to a minimum of about 1000 pairs at $z=0$.
    % Massive galaxies (right)
    The massive primary count (pink solid line in top right panel) behaves similarly to the dwarf primary count, with a minimum count at $z=4$ which rises to a maximum of $\sim2000$ halos per realization at $z\sim1$, then decreases slightly by $\sim5\%$ to $\sim$1800 halos by $z=0$. 
    Unlike dwarf pairs whose pair count peaks at $z=2$, pair count for massive galaxies (pink dashed line) follows similar behavior to the total massive primary count, with a minimum at $z=4$, and increasing to $z=\sim 1$ before leveling off. At very low redshift, the pair count and primary count have opposite behavior, with the pair count \textit{increasing} at very low redshifts of $z=0-0.25$ and \textit{peaking} at $z=0$.
    (Bottom) Fraction of pairs per primary as a function of redshift (i.e., the ratio between dotted line and solid line in each column). Dwarf and massive pair fractions are roughly flat for $z=2.5-4$, but display opposite behavior for $z=0-2.5$. The dwarf pair fraction decreases steadily from $\sim0.24$ to $\sim0.08$, a decrease of roughly $65\%$, while the massive pair fraction is roughly flat between $z=1-2.5$ with an average of $0.31$, before spiking sharply from $\sim 0.29$ to $\sim 0.36$ between $z=0-0.25$, an increase of $25\%$. 
    \todo{(replace with 1000 realizations fig)}
      }
    \label{fig:counts}
  \end{figure*}

  \begin{figure*}[htb]
    \centering
    \includegraphics[width=\textwidth]{stellarmass_distribution.png}
    \caption{\todo{caption, add z=4}
      }
    \label{fig:massratio}
  \end{figure*}

@@

\label{sec:results}
\begin{figure*}[htb]
  \centering
  \includegraphics[width=\textwidth]{pairratio.png}
  \caption{(Top) Median fraction (and 1-99 percentile shaded regions) of dwarf (green) or massive (pink) primaries with a major (left) or minor (right) companion. Shaded regions show the $$-$$ percentile range of the median pair fractions of each realization. 
  % 
  (Bottom) The median subtracted difference between the massive pair frction and the dwarf pair fraction, with the $$-$$ percentile range shaded. 
  The fraction of massive primaries with a major or minor companion remains approximately constant for $z>1$, and increases sharply  $z<\sim0.25$ the pair fraction increases sharply to $z=0$. However, the pair fraction for dwarf pairs evolves significantly differently to massive galaxy pairs. The fraction of dwarf primaries with a companion is approximately constant for $z>2$, but decreases monotonically from $z=2$ to $z=0$. \todo{finish caption, replace plot w 1000 reals vers., add 0 horizon} 
    }
  \label{fig:pairratio}
\end{figure*}

@@

\begin{figure*}[htb]
  \centering
  \includegraphics[width=\textwidth]{separation.png}
  \caption{Median physical separation (in kpc) and 1-99 percentile shaded regions of 1000 abundance matching realizations as a function of redshift for dwarf pairs (left, green), and massive pairs (right, pink). Major pairs (high stellar mass ratio) are shown in solid lines, while minor pairs are depicted with dashed lines. Minor dwarf pairs tend to be $\sim10-20\kpc$ closer than major dwarf pairs, while minor massive pairs are between $10-50\kpc$ closer than major pairs. In general, as the redshift \textit{decreases} toward $z=0$, the average physical separation of a dwarf or massive pair \textit{increases}. The evolution of massive pair separations is approximately linear for $z>1$, increasing sharply for $z<0$, while the evolution of the dwarf pairs closely resembles a power law distrbution across the whole redshift range from $z=0-4$. \todo{finish caption, replace with 1000 reals plot}
    }
  \label{fig:sep}
\end{figure*}

\begin{figure*}[htb]
  \centering
  \includegraphics[width=\textwidth]{separation_distribution.png}
  \caption{Normalized physical separation distribution for dwarf and massive pairs (top/green and bottom/pink, respectively) from $z=0$ (left) to $z=3$ (right). Major pairs are shown as solid lines, while minor pairs are dashed. 
  Both dwarf and massive pairs have narrow distributions about low separations at high redshifts, and a wider distribution of separations at lower redshift. 
  \kc{would it be instructive to make this plot, unnormalized, with z=0-3 on same plot to see if low sep pop numbers change drastically}
  Also note than many of the close pairs at high z may merge by $z=0$. \todo{change color of med lines, add z=4, replace with 1000 reals }
    }
  \label{fig:sep-dist}
\end{figure*}

\begin{figure*}[htb]
  \centering
  \includegraphics[width=\textwidth]{velocity.png}
  \caption{Median relative velocity (in \kms) and 1-99 percentile shaded regions of 1000 abundance matching realizations as a function of redshift for dwarf pairs (left, green) and massive pairs (right, pink). Major pairs (high stellar mass ratio) are shown in solid lines, while minor pairs are depicted with dashed lines. Major and minor pairs (in both the dwarf and massive regime) tend to have approximately the same median relative velocity. In addition, as the redshift \textit{decreases} toward $z=0$, the average relative velocity of a pair \textit{decreases} as well. The overall behavior of the redshift evolution is nearly identical for dwarf and massive pairs (though note that the massive pairs have \textit{much} higher relative velocities than the dwarf pairs at all redshifts.) \todo{reaplace with 1000 reals, finish caption, add 0 horizon line}
    }
  \label{fig:vel}
\end{figure*}

\begin{figure*}[htb]
  \centering
  \includegraphics[width=\textwidth]{velocity_distribution.png}
  \caption{
  Normalized velocity distribution for dwarf and massive pairs (top/green and bottom/pink, respectively) from $z=0$ (left) to $z=3$ (right). Major pairs are shown as solid lines, while minor pairs are dashed. 
  The distribution of relative velocities for dwarf and massive pairs move to slightly lower velocities at lower redshifts. The distribution of velocities for major and minor pairs is roughly equivalent. 
  \todo{finish caption, change color of med lines, add z=4, replace with 1000 reals }
    }
  \label{fig:vel-dist}
\end{figure*}

@@

\begin{figure*}[htb]
  \centering
  \includegraphics[width=\textwidth]{scaledsep.png}
  \caption{Median scaled separation (separation of a pair divided by the virial radius of its group) as a function of redshift. Dwarf pairs (major (solid) and minor (dashed)) tend to have smaller scaled separations at lower redshifts, leveling out between $z=0-1$. In particular, the secondaries of dwarf major pairs at $z>2$ tend to live more than one virial radius away from the primary. Massive major pairs at low redshift tend to have smaller scaled separations  at $z<\sim2$, but vary significantly at higher redshifts. 
  Minor pairs (right), both dwarf and massive, tend to have smaller separations, tending to live closer than one virial radius between the primary and secondary. Massive minor pairs tend to have smaller scaled separations compared to dwarf pairs at all redshifts.
  \todo{replace with 1000 reals fig, finish caption, add 0 horizon line}
    }
  \label{fig:sep-scaled}
\end{figure*}

\begin{figure*}[htb]
  \centering
  \includegraphics[width=\textwidth]{scaledsep_distribution.png}
  \caption{\todo{finish caption, 1000 reals, change median color, add z=4}}
  \label{fig:sep-scaled-dist}
\end{figure*}

\begin{figure*}[htb]
  \centering
  \includegraphics[width=\textwidth]{scaledvel.png}
  \caption{Median scaled velocity (relative velocity of a pair divided by the virial velocity), defined as the circular velocity at the virial radius of the group as a function of redshift. 
  Major pairs are on the left (solid lines), minor pairs are on the right in dashed lines.
  All sets of pairs show an increase in scaled velocity at lower redshifts.
  \todo{finish caption, replace with 1000 reals, add 0 horizon line}
  }
  \label{fig:vel-scaled}
\end{figure*}

\begin{figure*}[htb]
  \centering
  \includegraphics[width=\textwidth]{scaledvel_distribution.png}
  \caption{\todo{finish caption, 1000 reals, change median color, add z=4}}
  \label{fig:vel-scaled-dist}
\end{figure*}
